### 2023-11-10 main.tex
''
nonInt-chain

\sum_{\xi_{1}^{u(x)},\ldots,\xi_{a-1},\xi_{a+1},\ldots,\xi_{N-1}^{u(x)}=0}^{\infty}\sum_{\xi_{a}^{u(x)}=1}^{\infty}\left(\prod_{b=1}^{N-1}\left(\rho_{b}^{x}\right)^{\xi_{b}^{u(x)}}\right)\langle \xi_{1}^{u(x)},\ldots,\xi_{a}^{u(x)},\ldots,\xi_{N}^{u(x)}|(\mathbf{a}^{+})_{a}^{u(x)}\\=&

@@

&\sum_{\xi_{a}^{u(x)}=0}^{\infty}(\rho_{a}^{x})^{\xi_{a}^{u(x)}}\langle \xi_{1}^{u(x)},\ldots,\xi_{a}^{u(x)},\ldots,\xi_{N}^{u(x)}|(\mathbf{a}^{+})_{a}^{u(x)}\\=&\sum_{\xi_{a}^{u(x)}=1}^{\infty}(\rho_{a}^{x})^{\xi_{a}^{u(x)}}\langle \xi_{1}^{u(x)},\ldots,\xi_{a}^{u(x)},\ldots,\xi_{N}^{u(x)}|(\mathbf{a}^{+})_{a}^{u(x)}+\langle \xi_{1}^{u(x)},\ldots,0,\ldots,\xi_{N}^{u(x)}|(\mathbf{a}^{+})_{a}^{u(x)}\\=&\sum_{\xi_{a}^{u(x)}=1}^{\infty}(\rho_{a}^{x})^{\xi_{a}^{u(x)}}\langle \xi_{1}^{u(x)},\ldots,\xi_{a}^{u(x)},\ldots,\xi_{N}^{u(x)}|(\mathbf{a}^{+})_{a}^{u(x)}\dt

@@

 The first transformation $S_{1}$ is closely related to the duality matrix and we will see that $H^{'}$ is $\widetilde{H}^{T}$, up to the extra-site term described by the bosonic creation operator in \eqref{siteDualHamiltonian}. Therefore, $H^{'}$ is not stochastic. The second transformation $S_{2}$ diagonalizes the right boundary. Finally, the composition  $S_{2} S_{1}$ allows to simplify the commutators of the MPA algebra. 
\subsection{Explicit correlations in the non-equilibrium steady state}\label{subsection-exact}
In this section we write a formula for the stationary non-equilibrium steady state correlations between $m$- points of the chain, each of them occupied by a non-empty species, i.e. a species with label from $1$ to $N-1$.
\begin{theorem}[Explicit non-equilibrium steady state correlations]\label{thm-correlations}
Consider $m\in \{1,\ldots,L\}$ points with coordinates given by $(x_{1},\ldots,x_{m})$, such that $x_{k}<x_{k+1}$ $\forall k\in \{1,\ldots,m-1\}$. We assume that in each of these points there is a particle of species $a_{k}\in \{1,\ldots,N-1\}$. Then the $m$-point correlations with respect to the non-equilibrium steady state measure $\mu^{NESS}$ are given by 
\begin{equation}\label{exactCorrelations}
	\begin{split}
		&\mathbb{E}_{\mu^{\text{NESS}}}\left[\prod_{k=1}^{m}\mathbbm{1}_{\{\tau_{x_{k}}=a_{k}\}}\right]\\=&\sum_{t_{1},\ldots,t_{m}=0}^{1}\left(\prod_{k=1}^{m}\alpha_{a_{k}}^{t_{k}}\beta_{a_{k}}^{1-t_{k}}\right)\sum_{c_{1}=t_{1}}^{1}\ldots\sum_{c_{m}=t_{m}}^{1}f(L,c_{1},\ldots,c_{m})\left(\prod_{k=1}^{m}(-1)^{c_{k}-t_{k}}g_{k}(L,x_{k},c_{k},\ldots,c_{m})\right)
		\end{split}
\end{equation}
where
\begin{equation}\label{powerCoeffSpecies}
	g_{k}(L,x_{k},c_{k},\ldots,c_{m})=\left(L+2-x_{k}-\sum_{j=k}^{m}c_{j}\right)^{c_{k}}
\end{equation}
and 
\begin{equation}\label{powerCoeffNOspec}
	f(L,c_{1},\ldots,c_{m})=\frac{\Gamma(2+L-\sum_{a=1}^{m}c_{a})}{\Gamma(2+L)}
\end{equation}
Moreover, the absorption probabilities defined in \eqref{absProbabilitiesIntegrable} are
\begin{equation}\label{abs-probabilities}
	\mathcal{P}(t_{1},\ldots,t_{m},\bm{\xi})=\sum_{c_{1}=t_{1}}^{1}\ldots\sum_{c_{m}=t_{m}}^{1}f(L,c_{1},\ldots,c_{m})\prod_{j=1}^{m}(-1)^{c_{j}-t_{j}}g_{j}(L,x_{j},c_{j},\ldots,c_{m})
\end{equation}
where $\bm{\xi}=\sum_{k=1}^{m}\delta_{a_{k}}^{x_{k}}$.
\end{theorem}
\begin{comment}
 Consider . . Then, with respect to the non-equilibrium stationary distribution, the correlations among these particles are given by
\begin{equation}\label{exactCorrelations}
	\mathbb{E}_{\mu^{\text{NESS}}}\left[\prod_{k=1}^{m}\mathbbm{1}_{\{\tau_{x_{k}}=a_{k}\}}\right]=\sum_{c_{1},\ldots,c_{m}=0}^{1}
	f(L,c_{1},\ldots,c_{m})\prod_{k=1}^{m}(\alpha_{a_{k}}-\beta_{a_{k}})^{c_{k}}\beta_{a_{k}}^{1-c_{k}}g_{k}(L,y_{k},c_{k},\ldots,c_{m})
\end{equation}
\end{comment}
\begin{comment}
where 
\begin{equation}\label{powerCoeffSpecies}
	g_{k}(L,x_{k},c_{k},\ldots,c_{m})=\left(L+2-x_{k}-\sum_{j=k}^{m}c_{j}\right)^{c_{k}}
\end{equation}
and 
\begin{equation}\label{powerCoeffNOspec}
	f(L,c_{1},\ldots,c_{m})=\frac{\Gamma(2+L-\sum_{a=1}^{m}c_{a})}{\Gamma(2+L)}
\end{equation}
\end{comment}

@@

We consider the average with respect to $\mu^{NESS}$ of the occupation variable of the species $a_{1}\in \{1,\ldots,N-1\}$ at coordinate $x_{1}\in \{1,\ldots,L\}$. %This reads

@@

%\mathbb{E}_{\mu^{NESS}}\left[\mathbbm{1}_{\{\tau_{x_{1}}=a_{1}\}}\right]=\sum_{t_{1}=0}^{1}\alpha_{a_{1}}^{t_{1}}\beta_{a_{1}}^{1-t_{1}}\sum_{c_{1}=t_{1}}^{1}f(L,c_{1})g_{a_{1}}(L,x_{1},c_{1})\dt

@@

	 \mathbb{E}_{\mu^{NESS}}\left[\mathbbm{1}_{\{\tau_{x_{1}}=a_{1}\}}\right]=\frac{(L+1-x_{1})}{L+1}(\alpha_{a_{1}}-\beta_{a_{1}})+\beta_{a_{1}}\dt

@@

We consider the average with respect to $\mu^{NESS}$ of the occupation variable of the species  $a_{1},a_{2}\in \{1,\ldots,N-1\}$ at coordinates $x_{1},x_{2}\in \{1,\ldots,L\}$ such that $x_{1}< x_{2}$. 

@@

%		 \mathbb{E}_{\mu^{NESS}}\left[\mathbbm{1}_{\{\tau_{x_{1}}=a_{1}\}}\mathbbm{1}_{\{\tau_{x_{2}}=a_{2}\}}\right]= \sum_{t_{1}=0}^{1}\sum_{t_{2}=0}^{1}\left(\prod_{k=1}^{2}\alpha_{a_{k}}^{t_{k}}\beta_{a_{k}}^{1-t_{k}}\right)\sum_{c_{1}=t_{1}}^{1}\sum_{c_{2}=t_{2}}^{1}f(L,c_{1},c_{2})\prod_{j=1}^{2}g_{k}(L,x_{j},c_{j},c_{2})\dt

@@

	 \mathbb{E}_{\mu^{NESS}}\left[\mathbbm{1}_{\{\tau_{x_{1}}=a_{1}\}}\mathbbm{1}_{\{\tau_{x_{2}}=a_{2}\}}\right]&=\beta_{a_{1}}\beta_{a_{2}}+\frac{(L+1-y_{1})}{L+1}(\alpha_{a_{1}}-\beta_{a_{1}})\beta_{a_{2}}+\frac{(L+1-x_{2})}{L+1}(\alpha_{a_{2}}-\beta_{a_{2}})\beta_{a_{1}}\\&+\frac{(L-x_{1})(L+1-x_{2})}{L(L+1)}(\alpha_{a_{1}}-\beta_{a_{1}})(\alpha_{a_{2}}-\beta_{a_{2}})\dt

@@

		 \mathbb{E}_{\mu^{NESS}}\left[\mathbbm{1}_{\{\tau_{x_{1}}=a_{1}\}}\mathbbm{1}_{\{\tau_{x_{2}}=a_{2}\}}\right]-\prod_{k=1}^{2}\mathbb{E}_{\mu^{NESS}}\left[\mathbbm{1}_{\{\tau_{x_{k}}=a_{k}\}}\right]=-\frac{x_{1}(L-x_{2}+1)}{L(L+1)^{2}}\left(\alpha_{a_{1}}-\beta_{a_{1}}\right)\left(\alpha_{a_{2}}-\beta_{a_{2}}\right)\dt

@@

We consider the average with respect to $\mu^{NESS}$ of the occupation variable of the species  $a_{1},a_{2},a_{3}\in \{1,\ldots,N-1\}$ at coordinates $x_{1},x_{2},x_{3}\in \{1,\ldots,L\}$ such that $x_{1}<x_{2}<x_{3}$. Using \eqref{abs-probabilities} we compute the absorption probabilities 

@@

 \mathbb{E}_{\mu^{NESS}}\left[\prod_{k=1}^{3}\mathbbm{1}_{\{\tau_{x_{k}}=a_{k}\}}\right]&=\beta_{a_{1}}\beta_{a_{2}}\beta_{a_{3}}+\frac{(L+1-x_{1})}{(L+1)}(\alpha_{a_{1}}-\beta_{a_{1}})\beta_{a_{2}}\beta_{a_{3}}

@@

	&\mathbb{E}_{\mu^{NESS}}\left[\prod_{k=1}^{3}\mathbbm{1}_{\{\tau_{x_{k}}=a_{k}\}}\right]+2\prod_{k=1}^{3}\mathbb{E}_{\mu^{NESS}}\left[\mathbbm{1}_{\{\tau_{x_{k}}=a_{k}\}}\right]\nonumber\\-&\mathbb{E}_{\mu^{NESS}}\left[\mathbbm{1}_{\{\tau_{x_{1}}=a_{1}\}}\mathbbm{1}_{\{\tau_{x_{2}}=a_{2}\}}\right]\mathbb{E}_{\mu^{NESS}}\left[\mathbbm{1}_{\{\tau_{x_{3}}=a_{3}\}}\right]\nonumber\\
	-&\mathbb{E}_{\mu^{NESS}}\left[\mathbbm{1}_{\{\tau_{x_{1}}=a_{1}\}}\mathbbm{1}_{\{\tau_{x_{3}}=a_{3}\}}\right]\mathbb{E}_{\mu^{NESS}}\left[\mathbbm{1}_{\{\tau_{x_{2}}=a_{2}\}}\right]\nonumber\\
	-&\mathbb{E}_{\mu^{NESS}}\left[\mathbbm{1}_{\{\tau_{x_{2}}=a_{2}\}}\mathbbm{1}_{\{\tau_{x_{3}}=a_{3}\}}\right]\mathbb{E}_{\mu^{NESS}}\left[\mathbbm{1}_{\{\tau_{x_{1}}=a_{1}\}}\right]\nonumber

@@

In this subsection we specialize the results of Subsection \ref{statementDualitySubsection} to a chain of length $L$, where two reservoirs are attached to sites $1$ and $L$. Each site can still host $\nu\geq 1$ particles, chosen among the $N$ types. Now the dual graph is still a chain, but where two extra-sites $0$ (connected to $1$) and $L+1$ (connected to $L$) are present. As already pointed out the dual process eventually voids the chain by piling up particles of species $\{1,\ldots,N-1\}$ in the extra sites ($0$ and $L+1$) and replacing them by types $N$. This property allows to characterize the steady state non-equilibrium distribution (assuming that it is unique) by the probability that dual particles are absorbed in the extra-sites, then called \textit{absorption probabilities}. \\The process $\left(\bm{n}(t)\right)_{t\geq0}$ is defined on the space

@@

\begin{comment}
, i.e.
\begin{equation}\label{dualityFunctionChain}
	D(\bm{n},\bm{\xi})=\prod_{a=1}^{N-1}\left(\rho_{a}^{L}\right)^{\xi_{a}^{0}}\prod_{x=1}^{L}\frac{(\nu-\sum_{a=1}^{N-1}\xi_{a}^{x})!}{\nu!}\prod_{a=1}^{N-1}\frac{\eta_{a}^{x}!}{(n_{a}^{x}-\xi_{a}^{x})!}\prod_{a=1}^{N-1}\left(\rho_{a}^{R}\right)^{\xi_{a}^{L+1}}
\end{equation}
where $\rho_{\alpha}^{L}=\frac{\alpha_{a}}{|\alpha|}$ and where $\rho_{\alpha}^{R}=\frac{\beta_{a}}{|\beta|}$.\\
\end{comment}
The dual process has absorbing boundaries, i.e. all dual particles are eventually absorbed at $0$ or at $L+1$ with a certain probability. This implies that the chain is eventually voided and the steady state correlations of the original process can be written via the absorption probabilities of the dual process as explained in the following. 
We call $\mu^{NESS}$ the stationary measure of the the process $(\bm{n}(t))_{t\geq 0}$. For every $m\in\{1,\ldots,L\}$ we consider the dual configuration  $\bm{\xi}=\sum_{k=1}\delta_{a_{k}}^{x_{k}}$ with $x_{k}\in\{1,\ldots,L\}$ and $a_{k}\in \{1,\ldots,N-1\}$ for every $k\in \{1,\ldots,m\}$. The following  equalities holds using duality relation \eqref{duality-expectation}:
\begin{equation}\label{ExptationSS}
	\begin{split}
		\mathbb{E}_{\mu^{NESS}}\left[D(\bm{n}(t),\bm{\xi})\right]&=\lim_{t\to\infty}\mathbb{E}_{\bm{n}}\left[D(\bm{n}(t),\bm{\xi})\right]=\lim_{t\to\infty}\mathbb{E}_{\bm{\xi}}\left[D(\bm{n},\bm{\xi}(t))\right]
		\\&=
		\sum_{t_{1}=0}^{|\xi_{1}|}\ldots\sum_{t_{N}=0}^{|\xi_{N}|}\prod_{a=1}^{N-1}\left(\rho_{a}^{L}\right)^{t_{a}}\left(\rho_{a}^{R}\right)^{|\xi_{a}|-t_{a}}\mathcal{P}(t_{1},\ldots,t_{N},\bm{\xi})
	\end{split}
\end{equation}
where  $\rho_{\alpha}^{L}=\frac{\alpha_{a}}{|\alpha|}$, $\rho_{\alpha}^{R}=\frac{\beta_{a}}{|\beta|}$ and where 
\begin{equation}\label{Pass} 
	\mathcal{P}(i_{1},\ldots,i_{N},\bm{\xi})	=\mathbb{P}\left(\bm{\xi}(\infty)=\sum_{a=1}^{N-1}\left(t_{a}\delta_{0}+(|\xi_{a}|-t_{a})\delta_{L+1}\right)| \bm{\xi}(0)=\bm{\xi}\right)
\end{equation}
are the absorption probabilities for the non-integrable chain, i.e. the probabilities that $t_{a}$ particles of species $a$ are absorbed at $\{0\}$. Here we denoted $|\xi_{a}|=\sum_{x=1}^{L}\xi_{a}^{x_{k}}$.
The duality function \eqref{dualityElements} computed in the dual configurations $\bm{\xi}$ is given by 
\begin{equation}
	D(\bm{n},\bm{\xi})= \frac{\prod_{k=1}^{m}n_{a_{k}}^{x_{k}}}{(\nu-m+1)}\dt
\end{equation}
Therefore, up to a constant, $\mathbb{E}_{\mu^{\text{stat}}}\left[D(\bm{n},\bm{\xi})\right]$ gives the non-equilibrium steady state $m-$points correlations. This expectation can be computed by \eqref{ExptationSS} once the absorption probabilities are known. However, these absorption probabilities fulfil some difference equations that are not easy to solve. For example, we report in Appendix \ref{appendix-1pts-general} the solution for the simplest case of one point correlations that is exactly solvable, since the single dual particle behaves as an independent random walker.

@@

\section{One point correlations for the $\nu\geq 1$ case}\label{appendix-1pts-general}
We consider $\widehat{\bm{\xi}}=\delta_{s}^{y}$, then 
	\nu D(\eta,\delta_{s}^{y})=n_{s}^{y}\dt

@@

		\langle n_{s}^{x}\rangle_{\text{stat}}&=\frac{1}{\nu}\lim_{t\to\infty}\mathbb{E}_{\bm{n}}\left[D(\bm{n}(t),\delta_{s}^{y})\right]\\&=\frac{1}{\nu}\sum_{i_{s}=0}^{1}\left(\rho_{s}^{L}\right)^{i_{s}}\left(\rho_{s}^{R}\right)^{1-i_{s}}\mathbb{P}_{\delta_{s}^{y}}\left(\xi_{\infty}=i_{s}\delta_{0}+(1-i_{s})\delta_{L+1}\right)\dt

>>>>

%\sum_{\xi_{1}^{u(x)},\ldots,\xi_{a-1},\xi_{a+1},\ldots,\xi_{N-1}^{u(x)}=0}^{\infty}\sum_{\xi_{a}^{u(x)}=1}^{\infty}\left(\prod_{b=1}^{N-1}\left(\rho_{b}^{x}\right)^{\xi_{b}^{u(x)}}\right)\langle \xi_{1}^{u(x)},\ldots,\xi_{a}^{u(x)},\ldots,\xi_{N}^{u(x)}|(\mathbf{a}^{+})_{a}^{u(x)}\\=&

@@

&\sum_{\xi_{a}^{u(x)}=0}^{\infty}(\rho_{a}^{x})^{\xi_{a}^{u(x)}}\langle \xi_{1}^{u(x)},\ldots,\xi_{a}^{u(x)},\ldots,\xi_{N}^{u(x)}|(\mathbf{a}^{+})_{a}^{u(x)}
%=&\sum_{\xi_{a}^{u(x)}=1}^{\infty}(\rho_{a}^{x})^{\xi_{a}^{u(x)}}\langle \xi_{1}^{u(x)},\ldots,\xi_{a}^{u(x)},\ldots,\xi_{N}^{u(x)}|(\mathbf{a}^{+})_{a}^{u(x)}+\langle \xi_{1}^{u(x)},\ldots,0,\ldots,\xi_{N}^{u(x)}|(\mathbf{a}^{+})_{a}^{u(x)}\\
=\sum_{\xi_{a}^{u(x)}=1}^{\infty}(\rho_{a}^{x})^{\xi_{a}^{u(x)}}\langle \xi_{1}^{u(x)},\ldots,\xi_{a}^{u(x)},\ldots,\xi_{N}^{u(x)}|(\mathbf{a}^{+})_{a}^{u(x)}\dt
since
\langle \xi_{1}^{u(x)},\ldots,0,\ldots,\xi_{N}^{u(x)}|(\mathbf{a}^{+})_{a}^{u(x)}=0\dt

@@

 The first transformation $S_{1}$ is closely related to the duality matrix and we will see that $H^{'}$ is $\widetilde{H}^{T}$, up to the extra-site term described by the bosonic creation operator in \eqref{siteDualHamiltonian}. Therefore, $H^{'}$ is not stochastic. The second transformation $S_{2}$ diagonalizes the right boundary. Finally, the composition  $S_{2} S_{1}$ allows to simplify the commutators of the MPA algebra. 
\subsection{Explicit correlations in the non-equilibrium steady state}\label{subsection-exact}
In this section we write a formula for the stationary non-equilibrium steady state correlations between $m$- points of the chain, each of them occupied by a non-empty species, i.e. a species with label from $1$ to $N-1$.
\begin{theorem}[Explicit non-equilibrium steady state correlations]\label{thm-correlations}
Consider $m\in \{1,\ldots,L\}$ points with coordinates given by $(x_{1},\ldots,x_{m})$, such that $x_{k}<x_{k+1}$ $\forall k\in \{1,\ldots,m-1\}$. We assume that in each of these points there is a particle of species $a_{k}\in \{1,\ldots,N-1\}$. Then the $m$-point correlations with respect to the non-equilibrium steady state measure $\mu^{\text{NESS}}$ are given by 
\begin{equation}\label{exactCorrelations}
	\begin{split}
		&\mathbb{E}_{\mu^{\text{NESS}}}\left[\prod_{k=1}^{m}\mathbbm{1}_{\{\tau_{x_{k}}=a_{k}\}}\right]\\=&\sum_{t_{1},\ldots,t_{m}=0}^{1}\left(\prod_{k=1}^{m}\alpha_{a_{k}}^{t_{k}}\beta_{a_{k}}^{1-t_{k}}\right)\sum_{c_{1}=t_{1}}^{1}\ldots\sum_{c_{m}=t_{m}}^{1}f(L,c_{1},\ldots,c_{m})\left(\prod_{k=1}^{m}(-1)^{c_{k}-t_{k}}g_{k}(L,x_{k},c_{k},\ldots,c_{m})\right)
		\end{split}
\end{equation}
where
\begin{equation}\label{powerCoeffSpecies}
	g_{k}(L,x_{k},c_{k},\ldots,c_{m})=\left(L+2-x_{k}-\sum_{j=k}^{m}c_{j}\right)^{c_{k}}
\end{equation}
and 
\begin{equation}\label{powerCoeffNOspec}
	f(L,c_{1},\ldots,c_{m})=\frac{\Gamma(2+L-\sum_{a=1}^{m}c_{a})}{\Gamma(2+L)}
\end{equation}
Moreover, the absorption probabilities defined in \eqref{absProbabilitiesIntegrable} are
\begin{equation}\label{abs-probabilities}
	\mathcal{P}(t_{1},\ldots,t_{m},\bm{\xi})=\sum_{c_{1}=t_{1}}^{1}\ldots\sum_{c_{m}=t_{m}}^{1}f(L,c_{1},\ldots,c_{m})\prod_{j=1}^{m}(-1)^{c_{j}-t_{j}}g_{j}(L,x_{j},c_{j},\ldots,c_{m})
\end{equation}
where $\bm{\xi}=\sum_{k=1}^{m}\delta_{a_{k}}^{x_{k}}$.
\end{theorem}
\begin{comment}
 Consider . . Then, with respect to the non-equilibrium stationary distribution, the correlations among these particles are given by
\begin{equation}\label{exactCorrelations}
	\mathbb{E}_{\mu^{\text{NESS}}}\left[\prod_{k=1}^{m}\mathbbm{1}_{\{\tau_{x_{k}}=a_{k}\}}\right]=\sum_{c_{1},\ldots,c_{m}=0}^{1}
	f(L,c_{1},\ldots,c_{m})\prod_{k=1}^{m}(\alpha_{a_{k}}-\beta_{a_{k}})^{c_{k}}\beta_{a_{k}}^{1-c_{k}}g_{k}(L,y_{k},c_{k},\ldots,c_{m})
\end{equation}
\end{comment}
\begin{comment}
where 
\begin{equation}\label{powerCoeffSpecies}
	g_{k}(L,x_{k},c_{k},\ldots,c_{m})=\left(L+2-x_{k}-\sum_{j=k}^{m}c_{j}\right)^{c_{k}}
\end{equation}
and 
\begin{equation}\label{powerCoeffNOspec}
	f(L,c_{1},\ldots,c_{m})=\frac{\Gamma(2+L-\sum_{a=1}^{m}c_{a})}{\Gamma(2+L)}
\end{equation}
\end{comment}

@@

We consider the average with respect to $\mu^{\text{NESS}}$ of the occupation variable of the species $a_{1}\in \{1,\ldots,N-1\}$ at coordinate $x_{1}\in \{1,\ldots,L\}$. %This reads

@@

%\mathbb{E}_{\mu^{\text{NESS}}}\left[\mathbbm{1}_{\{\tau_{x_{1}}=a_{1}\}}\right]=\sum_{t_{1}=0}^{1}\alpha_{a_{1}}^{t_{1}}\beta_{a_{1}}^{1-t_{1}}\sum_{c_{1}=t_{1}}^{1}f(L,c_{1})g_{a_{1}}(L,x_{1},c_{1})\dt

@@

	 \mathbb{E}_{\mu^{\text{NESS}}}\left[\mathbbm{1}_{\{\tau_{x_{1}}=a_{1}\}}\right]=\frac{(L+1-x_{1})}{L+1}(\alpha_{a_{1}}-\beta_{a_{1}})+\beta_{a_{1}}\dt

@@

We consider the average with respect to $\mu^{\text{NESS}}$ of the occupation variable of the species  $a_{1},a_{2}\in \{1,\ldots,N-1\}$ at coordinates $x_{1},x_{2}\in \{1,\ldots,L\}$ such that $x_{1}< x_{2}$. 

@@

%		 \mathbb{E}_{\mu^{\text{NESS}}}\left[\mathbbm{1}_{\{\tau_{x_{1}}=a_{1}\}}\mathbbm{1}_{\{\tau_{x_{2}}=a_{2}\}}\right]= \sum_{t_{1}=0}^{1}\sum_{t_{2}=0}^{1}\left(\prod_{k=1}^{2}\alpha_{a_{k}}^{t_{k}}\beta_{a_{k}}^{1-t_{k}}\right)\sum_{c_{1}=t_{1}}^{1}\sum_{c_{2}=t_{2}}^{1}f(L,c_{1},c_{2})\prod_{j=1}^{2}g_{k}(L,x_{j},c_{j},c_{2})\dt

@@

	 \mathbb{E}_{\mu^{\text{NESS}}}\left[\mathbbm{1}_{\{\tau_{x_{1}}=a_{1}\}}\mathbbm{1}_{\{\tau_{x_{2}}=a_{2}\}}\right]&=\beta_{a_{1}}\beta_{a_{2}}+\frac{(L+1-y_{1})}{L+1}(\alpha_{a_{1}}-\beta_{a_{1}})\beta_{a_{2}}+\frac{(L+1-x_{2})}{L+1}(\alpha_{a_{2}}-\beta_{a_{2}})\beta_{a_{1}}\\&+\frac{(L-x_{1})(L+1-x_{2})}{L(L+1)}(\alpha_{a_{1}}-\beta_{a_{1}})(\alpha_{a_{2}}-\beta_{a_{2}})\dt

@@

		 \mathbb{E}_{\mu^{\text{NESS}}}\left[\mathbbm{1}_{\{\tau_{x_{1}}=a_{1}\}}\mathbbm{1}_{\{\tau_{x_{2}}=a_{2}\}}\right]-\prod_{k=1}^{2}\mathbb{E}_{\mu^{\text{NESS}}}\left[\mathbbm{1}_{\{\tau_{x_{k}}=a_{k}\}}\right]=-\frac{x_{1}(L-x_{2}+1)}{L(L+1)^{2}}\left(\alpha_{a_{1}}-\beta_{a_{1}}\right)\left(\alpha_{a_{2}}-\beta_{a_{2}}\right)\dt

@@

We consider the average with respect to $\mu^{\text{NESS}}$ of the occupation variable of the species  $a_{1},a_{2},a_{3}\in \{1,\ldots,N-1\}$ at coordinates $x_{1},x_{2},x_{3}\in \{1,\ldots,L\}$ such that $x_{1}<x_{2}<x_{3}$. Using \eqref{abs-probabilities} we compute the absorption probabilities 

@@

 \mathbb{E}_{\mu^{\text{NESS}}}\left[\prod_{k=1}^{3}\mathbbm{1}_{\{\tau_{x_{k}}=a_{k}\}}\right]&=\beta_{a_{1}}\beta_{a_{2}}\beta_{a_{3}}+\frac{(L+1-x_{1})}{(L+1)}(\alpha_{a_{1}}-\beta_{a_{1}})\beta_{a_{2}}\beta_{a_{3}}

@@

	&\mathbb{E}_{\mu^{\text{NESS}}}\left[\prod_{k=1}^{3}\mathbbm{1}_{\{\tau_{x_{k}}=a_{k}\}}\right]+2\prod_{k=1}^{3}\mathbb{E}_{\mu^{\text{NESS}}}\left[\mathbbm{1}_{\{\tau_{x_{k}}=a_{k}\}}\right]\nonumber\\-&\mathbb{E}_{\mu^{\text{NESS}}}\left[\mathbbm{1}_{\{\tau_{x_{1}}=a_{1}\}}\mathbbm{1}_{\{\tau_{x_{2}}=a_{2}\}}\right]\mathbb{E}_{\mu^{\text{NESS}}}\left[\mathbbm{1}_{\{\tau_{x_{3}}=a_{3}\}}\right]\nonumber\\
	-&\mathbb{E}_{\mu^{\text{NESS}}}\left[\mathbbm{1}_{\{\tau_{x_{1}}=a_{1}\}}\mathbbm{1}_{\{\tau_{x_{3}}=a_{3}\}}\right]\mathbb{E}_{\mu^{\text{NESS}}}\left[\mathbbm{1}_{\{\tau_{x_{2}}=a_{2}\}}\right]\nonumber\\
	-&\mathbb{E}_{\mu^{\text{NESS}}}\left[\mathbbm{1}_{\{\tau_{x_{2}}=a_{2}\}}\mathbbm{1}_{\{\tau_{x_{3}}=a_{3}\}}\right]\mathbb{E}_{\mu^{\text{NESS}}}\left[\mathbbm{1}_{\{\tau_{x_{1}}=a_{1}\}}\right]\nonumber

@@

In this subsection we specialize the results of Subsection \ref{statementDualitySubsection} to a chain of length $L$, where two reservoirs are attached to sites $1$ and $L$. Each site can host $\nu\geq 1$ particles, chosen among the $N$ types. Now the dual graph is still a chain, but with two extra-sites $0$ (connected to $1$) and $L+1$ (connected to $L$). As already pointed out the dual process eventually voids the chain by piling up particles of species $\{1,\ldots,N-1\}$ in the extra sites ($0$ and $L+1$) and replacing them by types $N$. This property allows to characterize the steady state non-equilibrium distribution (that it is unique) by the probability that dual particles are absorbed in the extra-sites, called \textit{absorption probabilities}. The process $\left(\bm{n}(t)\right)_{t\geq0}$ is defined on the space

@@

, i.e.
The dual process has absorbing boundaries, i.e. all dual particles are eventually absorbed at $0$ or at $L+1$ with a certain probability. This implies that the chain is eventually voided and the steady state correlations of the original process can be written via the absorption probabilities of the dual process as explained in the following. 
We call $\mu^{\text{NESS}}$ the non-equilibrium stationary state measure of the the process $(\bm{n}(t))_{t\geq 0}$. For every $m\in\{1,\ldots,L\}$ we consider  $x_{k}\in\{1,\ldots,L\}$ and $a_{k}\in \{1,\ldots,N-1\}$ for every $k\in \{1,\ldots,m\}$ and we introduce the dual configuration  $\bm{\xi}=\sum_{k=1}^{m}\delta_{a_{k}}^{x_{k}}$ meaning that 
		\xi_{a}^{x}=\sum_{y=1}^{L}\sum_{b=1}^{N-1}\mathbbm{1}_{\{y=x_{k}\}}\mathbbm{1}_{\{b=b_{k}\}}\qquad &\text{if}\quad x=x_{k}\;\text{and} \; a=a_{k}\\
		\xi_{a}^{x}=0\qquad &\text{otherwise}
The duality function \eqref{dualityElements} computed in this dual configurations is 
	D(\bm{n},\bm{\xi})= \frac{\prod_{k=1}^{m}n_{a_{k}}^{x_{k}}}{C(\nu,m)}\dt
where $C(\nu,m)$ is a constant that depends on the number of correlated particles $m$ and on the maximal occupancy $\nu$. 
Therefore, up to this constant, $\mathbb{E}_{\mu^{\text{NESS}}}\left[D(\bm{n},\bm{\xi})\right]$ gives the non-equilibrium steady state $m-$points correlations. The following equalities hold using duality relation \eqref{duality-expectation}:
		\frac{\mathbb{E}_{\mu^{\text{NESS}}}\left[\prod_{k=1}^{m}n_{a_{k}}^{x_{k}}\right]}{C(\nu,m)}&=\lim_{t\to\infty}\mathbb{E}_{\bm{n}}\left[D(\bm{n}(t),\bm{\xi})\right]=\lim_{t\to\infty}\mathbb{E}_{\bm{\xi}}\left[D(\bm{n},\bm{\xi}(t))\right]
		\sum_{t_{1}=0}^{|\xi_{1}|}\ldots\sum_{t_{N}=0}^{|\xi_{N}|}\prod_{a=1}^{N-1}\left(\rho_{a}^{L}\right)^{t_{a}}\left(\rho_{a}^{R}\right)^{|\xi_{a}|-t_{a}}\mathcal{P}(t_{1},\ldots,t_{N},\bm{\xi})
where  $\rho_{\alpha}^{L}=\frac{\alpha_{a}}{|\alpha|}$, $\rho_{\alpha}^{R}=\frac{\beta_{a}}{|\beta|}$ are the boundary densities and 
	\mathcal{P}(t_{1},\ldots,t_{N},\bm{\xi})	=\mathbb{P}\left(\bm{\xi}(\infty)=\sum_{a=1}^{N-1}\left(t_{a}\delta_{a}^{0}+(|\xi_{a}|-t_{a})\delta_{a}^{L+1}\right)| \bm{\xi}(0)=\bm{\xi}\right)
are the absorption probabilities for the non-integrable chain, i.e. the probabilities that $t_{a}$ particles of species $a$ are absorbed at $\{0\}$. Here we denoted $|\xi_{a}|=\sum_{x=1}^{L}\xi_{a}^{x}$.
 This expectation can be computed by \eqref{ExptationSS} once the absorption probabilities are known.  For example, we report in Appendix \ref{appendix-1pts-general} the solution for the simplest case of one point correlations that is exactly solvable, since the single dual particle behaves as an independent random walker. However, these absorption probabilities for higher point correlations fulfil some difference equations that are not easy to solve.

@@

\section{One point correlations for $\nu\geq 1$}\label{appendix-1pts-general}
We take $m=1$ and we fix a site $x\in\{1,\ldots,L\}$ and a species $a\in \{1,\ldots,N-1\}$. We consider the dual configuration $\bm{\xi}=\delta_{a}^{x}$, then 
	\nu D(\eta,\delta_{a}^{x})=n_{a}^{x}\dt

@@

			\mathbb{E}_{\mu^{\text{NESS}}}\left[n_{a}^{x}\right]&=\nu\lim_{t\to\infty}\mathbb{E}_{\bm{n}}\left[D(\bm{n}(t),\delta_{a}^{x})\right]\\&=\nu\sum_{t_{a}=0}^{1}\left(\rho_{a}^{L}\right)^{t_{s}}\left(\rho_{s}^{R}\right)^{1-t_{s}}\mathbb{P}_{\delta_{a}^{x}}\left(\xi_{\infty}=t_{a}\delta_{0}+(1-t_{a})\delta_{L+1}\right)\dt
To explicitly find the result, we aim to determine $\mathcal{P}(1,\delta_{a}^{x})=\mathbb{P}_{\delta_{a}^{x}}\left(\xi_{\infty}=t_{a}\delta_{a}^{0}+(1-t_{a})\delta_{a}^{L+1}\right)$. This is the probability of a random walker on the chain $\{1,\ldots,L\}$ with absorbing boundaries, therefore, it fulfils the following equations discrete Laplace equation
